%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {\textbf{Associate Analyst}} % Job title
    {Red Foil Pvt Ltd} % Organization
    {Melbourne, Australia} % Location
    {May 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \normalsize{\item {Performed interpretation of data in order to identify seasonal and cyclic patterns to analyze new areas of opportunities and proposed solutions to improve system efficiency.}
      \item {Used statistical techniques for hypothesis testing to validate and interpret data and used visualization techniques for reporting data to clients.}
      \item {Handled projects with the development of design, mind map and procedures for delivering them promptly with our team remotely.}
      \item{Conducted post project launch evaluation with client to identify successful features and find ways to improve on them.}
      \item {Developed strong cross-functional relationships with clients and stakeholders across different levels.}}
        % \item {Developed a tool for Business analytics in MVP products of Gaggle for clients using Amazon Web services.}
        % \item {Developed an analytical tool utilising R Shiny for visualising the trend, seasonality patterns of sales and forecasting cash flow with impacts based on the client's historical data.}
        % \item {Performed data wrangling and exploratory data analysis for operational and financial data to identify new areas of opportunities for clients.}
        %\item {Designed a PCB in kicad and had the final board manufactured from a fab facility. This is a miniaturization of the original stack of boards.}
         %\item {Developed QT app for data collection for Mbient sensors.}
      \end{cvitems}
    }
    
  \cventry
    {\textbf{Analyst Intern}} % Job title
    {Star Health and Allied Insurance} % Organization
    {Chennai, India} % Location
    {Dec 2018 - Feb 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \normalsize{\item {Worked under the guidance of analyst team to developed ARIMA and Holt Winters models for forecasting the company’s claims target using large volume of data.}
        \item {Designed a fraud detection model which can potentially reduce 25\% wastage of organisation's claims.}
        \item {Used Informatica to perform claims management procedure and data audit for reporting.}}
        %\item {Designed a PCB in kicad and had the final board manufactured from a fab facility. This is a miniaturization of the original stack of boards.}
         %\item {Developed QT app for data collection for Mbient sensors.}
      \end{cvitems}
    }

  \cventry
    {\textbf{Search Engine Optimization Intern}} 
    {Avyukta Intellicall Consulting Pvt Ltd}
    {Chennai, India}
    {Jun 2017 - Aug 2017}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \normalsize{\item {Implemented keyword optimisation for client's web page and monitored through Google Analytics for generating weekly reports.}
        \item {Suitable ranking techniques using NLP were utilized to improve client's website rank in web search results.}}
        %\item {Selected as mentor to visit Google campus.}
        %\item {Reviewed work submitted by a student (code review, documentation review, javadocs, etc...)}
        %  \item { Helped students refine their work that actively improves Terasology}
      \end{cvitems}
    }

  \cventry
    {\textbf{Communication Engineering Intern}} % Job title
    {Chennai Metro Rail Limited} % Organization
    {Chennai, India} % Location
    { May 2015 - Jun 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \normalsize{\item {Assigned to the signalling department for monitoring faults present in the metro service lines and to maintain records of testing activities.}
        \item {Developed an user friendly interface for integrating Automatic Fare Collection hardware under the guidance of telecommunication team.}}
        %\item {Reviewed work submitted by a student (code review, documentation review, javadocs, etc...)}
        %  \item { Helped students refine their work that actively improves Terasology}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
