%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research \& Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {\textbf{Team Facilitator}} % Role
    {Access to Justice - Tenancy Trip} % Event
    {Monash University} % Location
    {Oct 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \normalsize{\item {Worked with cross cultural team and developed a web application in a span of 10 weeks for providing tenancy related information for new international students in the state of Victoria.}
        \item{\textbf{ASP.Net} with MVC architecture, \textbf{CSS} and \textbf{Javascript} for developing front-end application and \textbf{Python Flask framework} for implementing back-end functionalities which are hosted in Amazon Web service and Heroku app respectively.}}
        %\item{Application link - \url{http://tenancytrip.tk/}}
      \end{cvitems}
    }

  \cventry
    {\textbf{Data analyst}} % Role
    {Suggestive Spelling Correction for Document Retrieval } % Event
    {Monash University} % Location
    {Oct 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \normalsize{\item {A retrieval engine was built where all documents are read, stemmed and tokenised using \textbf{Python's NLTK package}.} 
        \item{\textbf{RegEx} were used to achieve a token list containing all matched patterns from the documents.}
        \item{Search ranking technique was implemented to rank all documents based on tf-idf weights, term frequencies and document frequencies.}
        \item{User’s query terms were spell checked before the retrieval process by obtaining all possible combinations of letters present in the term.}}
      \end{cvitems}
    }
\vspace{0.3cm}    
\cventry
    {\textbf{Data Analyst}} % Role
    {Formula One - Visual Data Exploration } % Event
    {Monash University} % Location
    {Sep 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \normalsize{\item{Using \textbf{R Shiny}, visualised the relationship between drivers and teams from the year 1950 to 2017 and visualised lap chart to analyse driver's performance for all Grand-Prix of season 2017.}
        \item{Using \textbf{Pandas} and \textbf{Numpy packages} in python, Data sets from various sources were wrangled and anomalies were fixed by imputing values for missing data, maintaining uniform structure of the data.}}
      \end{cvitems}
    }

%---------------------------------------------------------
% \cventry
%     {Personal} % Role
%     {Alchehistory ({\tiny play.google.com/store/apps/details?id=com.SmoketreeStudios.Trees.Alchehistory})} % Event
%     {} % Location
%     {} % Date(s)
%     {
%       A simple Match 3 game revolving around combining elements to form other elements and vice versa. This game was developed in unity3d and featured a selection of small self contained levels and an infinite mode of play.
%     }

\vspace{0.3cm}
\cventry
    {\textbf{Undergraduate Researcher}}
    {ANN Based Dis-fluent Speech Classification}
    {Anna University}
    {Jul 2016 - Apr 2017}
    {
     \begin{cvitems} % Description(s)
        \normalsize{\item {The classification of disfluency in speech was achieved by implementing a neural network model in \textbf{MatLab} which was trained by various voice samples.}
        \item{Real time voice samples were collected containing normal and stuttered speech which were analysed for obtaining speech features like cepstral coefficients and prosodic features.}
        \item{\href{https://www.jchps.com/specialissues/2017\%20Special\%20Issue\%2011/EC1766.pdf}{\textbf{Google Scholar link}, Journal Published on Journal of Chemical and Pharmaceutical Science, July 2017, ISSN: 0974-2115}}}
      \end{cvitems}
    }

\end{cventries}


